### 2016-01-16 paper.tex
Shorten title a bit more; towards #37

{\Large \textbf\newline{Experimental investigation of a low solidity cross-flow
        turbine at transitional Reynolds numbers: Power production, near-wake dynamics,
        and blade support strut losses}} \newline % Insert author names, affiliations
% and corresponding author email (do not
% include
% titles, positions, or degrees).
\\ Peter Bachant\textsuperscript{1,*}, Martin Wosnik\textsuperscript{1}, Budi
Gunawan\textsuperscript{2}, Vincent S. Neary\textsuperscript{2} \\ \bigskip \bf{1}
Center for Ocean Renewable Energy, University of New Hampshire, Durham, NH, USA
\\ \bf{2} Water Power Technologies, Sandia National Laboratories, P.O. Box 5800,
Albuquerque, New Mexico 87185-MS1124 \\ \bigskip

>>>>

{\Large \textbf\newline{Experimental investigation of a low solidity cross-flow
        turbine at transitional Reynolds numbers: Power production, strut losses, and
        near-wake dynamics}} \newline % Insert author names, affiliations
% and corresponding author email (do not
% include
% titles, positions, or degrees).
\\ Peter Bachant\textsuperscript{1,*}, Martin Wosnik\textsuperscript{1}, Budi
Gunawan\textsuperscript{2}, Vincent S. Neary\textsuperscript{2} \\ \bigskip
\bf{1} Center for Ocean Renewable Energy, University of New Hampshire, Durham,
NH, USA \\ \bf{2} Water Power Technologies, Sandia National Laboratories, P.O.
Box 5800, Albuquerque, New Mexico 87185-MS1124 \\ \bigskip
